GPU Acceleration of the Material Point Method

### 2019-02-12 pres/pres.tex
layouting

\begin{minipage}{0.31\textwidth}
  \tiny
\begin{minipage}{0.95\textwidth}
  SoA-Layout
\begin{lstlisting}[language={GLSL},style={GL},basicstyle=\tiny]
struct Container{
  vec4 positions[n];
  vec4 velocities[n];
} Particles;
\end{lstlisting}
\end{minipage}
\begin{minipage}{0.95\textwidth}
  AoS-Layout
\begin{lstlisting}[language={GLSL},style={GL},basicstyle=\tiny]
struct Particle {
  vec4 position;
  vec4 velocity;
} Particles[n];
\end{lstlisting}
\end{minipage}

\end{minipage}
\begin{minipage}{0.64\textwidth}
  \tiny
  \includesvg[svgpath =../images/,width=\textwidth]{soa}
  Structures of arrays(SoA)
  \\
  \includesvg[svgpath =../images/,width=\textwidth]{aos}
  Arrays of structures(AoS)

\end{minipage}
\end{frame}
\begin{frame}
\begin{table}[htbp]
  \begin{tabular}{ | l | l | l | l | l | l | l |}    \hline
    Layout &  $\Delta t_c (\mu s)$	& Speedup &VRAM     & SM     & L2     & SM Issue Util. \\\hline
    AoS         & 243                   & -       &77.7\%   & 7.3\%  & 30.3\% & 6.8\% \\\hline
    SoA         & \textbf{120}                   & 2.26x   &75.4\%   & \textbf{14.3}\% & 29.4\% & \textbf{14.0\%} \\
    \hline
\end{tabular}
\end{table}

  \end{frame}
\section{Delving Deeper: Further Opportunities}

>>>>

\begin{minipage}{0.31\textwidth}
\begin{minipage}{0.95\textwidth}
Coalescing:
\vspace*{23}
\end{minipage}
\tiny
\begin{minipage}{0.95\textwidth}
  SoA-Layout
\begin{lstlisting}[language={GLSL},style={GL},basicstyle=\tiny]
struct Container{
  vec4 positions[n];
  vec4 velocities[n];
} Particles;
\end{lstlisting}
\vspace*{29}
\end{minipage}
\begin{minipage}{0.95\textwidth}
  AoS-Layout
\begin{lstlisting}[language={GLSL},style={GL},basicstyle=\tiny]
struct Particle {
  vec4 position;
  vec4 velocity;
} Particles[n];
\end{lstlisting}
\end{minipage}
\end{minipage}
\begin{minipage}{0.64\textwidth}
  \tiny
  \includesvg[svgpath =../images/,width=\textwidth]{soa}
  Structures of arrays(SoA)
\\
  \includesvg[svgpath =../images/,width=\textwidth]{aos}
  Arrays of structures(AoS)

\end{minipage}
\end{frame}
\begin{frame}
Nvidia Nsight\cite{NVIDIA:METRICS} now offers metrics to identify bottlenecks:
\vspace{-5}
\begin{table}
  \footnotesize
  \begin{tabular}{ | l | l |}    \hline
    \textbf{Metric}   & \textbf{Description} \\ \hline
    VRAM SOL\%        & memory througput w.r.t. to hardware limit\\\hline
    SM SOL\%          & instruction throughput\\\hline
    L2 SOL\%          & L2-cache throughput\\\hline
    Tex SOL\%         & L1-cache throughput\\\hline
    SM Issue Util.\%  & amount of cycles an instr. was issued\\\hline
  \end{tabular}
\end{table}
\\
\vspace{5}
A simple map or copy shader with one instruction shows SoA vs. AoS differences:
\vspace{-15}
\begin{table}
  \footnotesize
  \begin{tabular}{ | l | l | l | l | l | l | l |}    \hline
    Layout &  $\Delta t_c (\mu s)$	& Speedup &VRAM     & SM     & L2     & SM Issue Util. \\\hline
    AoS         & 243                   & -       &77.7\%   & 7.3\%  & 30.3\% & 6.8\% \\\hline
    SoA         & \textbf{120}                   & 2.26x   &75.4\%   & \textbf{14.3}\% & 29.4\% & \textbf{14.0\%} \\
    \hline
\end{tabular}
\end{table}
$\Rightarrow$ SoA increases coalescing for non-random access.
\end{frame}
\subsection{Parallel Reduction \& Scan}
\begin{frame}
  \frametitle{Parallel Reduction \& Scan}
\end{frame}
\section{Delving Deeper: Further Opportunities}
